Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-02 manuscript.Rmd
updates - maps

# Could also directly import census demographic data using tidycensus package
demographic_data <- read.csv("data/DC_demographic_data.csv", header = FALSE)
names <- unlist(demographic_data[2,])
demographic_data <- demographic_data %>% 
  slice(3:8096)
head(demographic_data)
colnames(demographic_data) <- names
head(demographic_data)

@@

@@

>>>>

travel_times <- travel_times %>%
	mutate(origin_id = factor(origin_id),
				 dest_id = factor(dest_id))

head(travel_times)

@@

```{r}
demographic_data_big <- read.csv("data/DC_demographic_data.csv", header = FALSE)
names <- unlist(demographic_data_big[2,])
demographic_data_big <- demographic_data_big %>%
  slice(3:8096)
head(demographic_data_big)
colnames(demographic_data_big) <- names
demographic_data_big <- demographic_data_big %>%
  mutate(state = substr(geo2010, start = 1, stop = 2)) %>%
  mutate(tract_number = substr(geo2010, start = 10, stop = 1000)) %>% 
  filter(timeframe == "2012-16")
head(demographic_data_big)

```

```{r}
demographic_data_big %>% 
  filter(substr(tract_number, start = 1, stop = 2) == "2.")
```

Tidycensus package!!

```{r}

#tigris package - contains roads for DC
options(tigris_class="sf")
#primary_secondary_roads includes interstates and other highways in DC
dc_roads <- primary_secondary_roads(state= c("DC", "VA")) %>%
	st_transform(crs = 102285)
```

@@

```{r}
travel_time_sf %>% 
  mutate(state = substr(geo2010, start = 1, stop = 2)) %>%
  mutate(tract_number = substr(geo2010, start = 10, stop = 1000)) %>%
```

```{r map_acs}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = blackE)) +
	theme_map +
	scale_fill_viridis_c()
```

```{r map_acs}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = car_transitE)) +
	theme_map +
	scale_fill_viridis_c()
```
